Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-07-07 tex/paper1/paper1.tex
incorporated the latest suggestions from James and Andrew

\begin{abstract}
The \mFpa\ of regions of the solar corona are investigated using AIA
171\AA\ and 193\AA\ data.  It is shown that the \mFpa\ in all regions
show an approximate \PL\ behaviour.  This average behavior is
inconsistent with the common assumption that coronal time-series are
well described by the sum of a long time-scale background trend plus
Gaussian-distributed noise, with some specific locations also showing
an oscillatory signal.  The implications of this discovery to the
field of coronal seismology and automated detections of oscillations
is discussed.  Further, it is shown that the observed \PL\ \PS\ can be
formed by summing a distribution of exponentially decaying emission
events along the line of sight.  This is consistent with the notion
that the solar atmosphere is heated everywhere by small energy
deposition events.
\end{abstract}

@@

\section{Introduction}\label{sec:int}
Coronal seismology is the study of oscillatory phenomena in the solar
corona.  First suggested by \cite{1970PASJ...22..341U}, the practice
of coronal seismology attempts to locate oscillatory phenomena in the
solar corona, identify the wave modes present, and then use
theoretical descriptions of those wave modes to infer the physical
conditions of the solar corona.  The practice of coronal seismology
began in earnest with observations of wave modes by SOHO-EIT
\citep{1998ApJ...501L.217D, 1999SoPh..186..207B} and TRACE
\citep{1999ApJ...520..880A} (see also \cite{lrsp-2005-3},
\cite{2012RSPTA.370.3193D} for more extensive reviews of coronal
seismology).  Since then, many papers have been published describing
oscillatory phenomena in the corona and their interpretation in terms
of theoretically known wave modes.

@@

Their scarcity on the Sun has prompted efforts to create automated
oscillation detection algorithms.  The need for an automated
oscillation detection algorithm is also exacerbated by the large and
rapidly growing amount of AIA data, which means that the amount of
data that has to be searched is large.  There have been several
attempts at designing such algorithms, all of which operate on
time-series of two-dimensional image data (data cubes).
\cite{2004SoPh..223....1D} describe the design of an automated
oscillation-detection algorithm based on the wavelet analysis. The
algorithm finds significant wave packets ranging from single to
multiple wave cycles in duration, by a wavelet power/confidence level
comparison against the null hypothesis that a given time series is
Gaussian-distributed noise.  Pixels with significant oscillatory
content are grouped manually.  \cite{2007SoPh..241..397N} take a
similar approach, using a thresholded fast Fourier transform to find
locations in TRACE data that may support an oscillatory signal. The
threshold level is defined as three to four times the average FFT
power; if the maximum FFT power is above this level then the frequency
at which that power occurs is assumed to be real.
\cite{2010SoPh..264..403I} assume that an oscillatory signal is
present in each location in the datacube and then use a Bayesian-based
treatment to calculate the probability that the frequency has a
particular value.  This algorithm relies on subtracting a background
trend from the time-series being tested, and assumes that the noise is
Gaussian distributed.

The above algorithms precipitate detections based on the strength of
the signal of an oscillation on a pixel by pixel basis, and then group
these pixels together using some set of criteria.  The automated
detection algorithm of \cite{2008SoPh..248..395S} begins by
identifying candidate oscillatory regions as those that show a high
variance \citep{2003SoPh..213..103G} (under the implicit assumption
that the time-series has an approximately constant mean value).
Detections are based on wavelet filtering of these regions in all
three dimensions of the data cube simultaneously, with the implicit
assumption that the noise is Gaussian-distributed.  The algorithm of
\cite{2008SoPh..252..321M} differs from the previous algorithms: it
begins by Fourier transforming the entire data cube, and calculating
the coherence of neighboring pixels in narrow frequency bands, and
filtering the results. The null hypothesis here is that the time
series is pure Gaussian noise, with the additional assumption that
pairs of noisy time-series have low coherence, and so can be rejected.
In this algorithm, the spatial extent of the coherence of the
oscillatory signal is the key identifier of a wave process.

@@

\section{Observations}\label{sec:obs}
The data used in this study is from AIA on board the Solar Dynamics
Observatory (SDO).  AIA observes images of the Sun in multiple
wavebands simultaneously and continuously, at high cadence (12
seconds) and at high spatial resolution (0.6 arcseconds per pixel at
the Sun).  These data enable detailed comparisons between phenomena
seen in multiple wavebands, and are therefore ideal for assessing the
frequency content of the solar atmosphere.  The data was acquired
using the Lockheed Martin Solar Astrophysics cutout service
(http://lmsal.com/get\_aia\_data/).  Six hours of image data in the
time range 2012-09-23 00:00 - 06:00 UT, at the full 12 second cadence,
in the 171\AA and 193\AA\ wavebands is used.  These wavebands were
selected because previous studies in similar wavebands (TRACE 171\AA
and 193\AA) show the presence of coronal oscillations.  The cutout of
the Sun selected covers two adjacent $\beta\gamma$ regions NOAA AR
11575 and AR 11577.  This cutout was selected for two reasons.  First,
it is quiescent in that there were no X-ray flares or other
large-scale disturbances over the spatial extent of the cutout within
the time range.  Therefore, any variations in the plasma properties
cannot be ascribed to large-scale disturbances.  Second, the selected
cutout region contains a sunspot, and sunspots are known to be
locations over which three minute oscillations have been detected by
other instruments \citep{2002A&A...387L..13D}.

The downloaded cutout data was prepared for analysis using the
SolarSoft / IDL routines READ\_SDO and AIA\_PREP.  These procedures
convert the downloaded level 1.0 FITS cutout files to level 1.5 FITS
files.  This involves translating, scaling and rotating the images so
they have the same sun-center, image scale with solar north in the
same direction.  All further processing from this point was performed
in the SunPy 0.4 (http://www.sunpy.org) data analysis environment.
Images were de-rotated to compensate for solar rotation, based on the
center of the field of view of each image.  After de-rotation, each
image layer was co-registered with the image half way through the
dataset, at approximately 03:00 UT.

\section{Analysis}\label{sec:anal}
We wish to analyze the frequency content of these resulting datacubes
as a function of spatial location.  Four locations were chosen in the
data representing four different types of physical locations in the
solar atmosphere.  These were a quiet Sun region, a region that lies
on top of a sunspot, a footpoint region, and a coronal moss region.
Figures \ref{fig:loc171193} show the location of the regions on sample
images from the time range considered.

@@

Consider the emission from a single pixel, $I(t)$.  The Fourier power
spectrum for this emission was calculated as follows.  First, the
time-series was normalized by calculating $(I(t) - \langle I(t)
\rangle)/\langle I(t) \rangle$. Secondly, the normalized time-series
was apodized using the Hanning window, reducing ringing effects in the
\PS.  The full 12 second cadence is used, yielding time series of 1800
samples.  The full spatial resolution is also retained in order to
obtain fine detail on the variation of frequency content as a function
of location.  Figures \ref{fig:compare171193} show example power
spectra, plotted using a log-log scale, from a single location inside
each of the regions shown in Figure \ref{fig:loc171193}.  The shape of
the power spectra indicate that the Fourier power approximately
follows a \PL\ at lower frequencies, and flattens out at higher
frequencies.

@@

\begin{figure}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.power_spectra_distributions.eps}
}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.power_spectra_distributions.eps}
}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.power_spectra_distributions.eps}
}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.power_spectra_distributions.eps}
}
\caption{Distribution of Fourier power at some sample frequencies as a
function of AIA waveband and location.}
\label{fig:dist171193}
\end{figure}
Figure \ref{fig:dist171193} show the distributions of the logarithm of
the Fourier power for a small number of frequencies, for all the
pixels in each region.  These distributions are centrally peaked, and
show a slightly heavier tail towards lower Fourier powers (negative
skew), and are slightly broader when compared to a Gaussian
distribution.  Plots of all these distribution show that they are all
unimodal.  These observations guide the choice of how to average the
\PS\ over each of the selected region.  The nature of these
distributions suggest that the arithmetic mean of the Fourier power is
biased by the very largest powers.  Therefore, the mean value of the
logarithm of the Fourier power is a better description of the range of
values in the data (this is equivalent to the geometric mean of the
Fourier power).  The \PA\ used below are calculated from the mean
value of the logarithm of the Fourier power.

@@

The (geometric) \mFpa\ are shown in Figure \ref{fig:fit171193} for
each of the physical regions considered.  It is clear that, in
general, the \mFpa\ exhibit power-law like characteristics.  The
results for the quiet Sun, loop footpoints and sunspot regions suggest
a \PL\ \PS.  This can be modeled as
\begin{equation}
\label{eqn:pwrlaw}
\mbox{Model $M_{1}$}: P_{1}(\nu) = A\nu^{-n} + C,
\end{equation}
where $\nu$ is the normalized frequency, $A>0$ is a proportionality
constant and $n>0$ is the \PL\ index.  The quantity $C>0$ models
the high-frequency / low power end of the spectrum where the detection
properties of the detector apparatus are assumed to dominate the
observations.

@@

Model selection is implemented using the Akaike Information Criterion
(AIC) and the Bayesian Information Criterion (BIC)
\citep{2007MNRAS.377L..74L, WICS:WICS199}.  The AIC is defined as
\begin{equation}\label{eqn:aic}
AIC \equiv -2 \ln L_{max} - 2k
\end{equation}
where $L_{max}$ is the maximum likelihood achievable by the model, and
$k$ is the number of parameters in the model ($k=3$ for Model 1, and
$k=6$ for Model 2).  The BIC is defined as
\begin{equation}\label{eqn:bic}
BIC \equiv -2 \ln L_{max} - k\ln N
\end{equation}
where $N$ is the number of data points used in the fit (in this case
$N=899$, the number of non-zero frequencies of the Fourier power
spectrum).  Model selection is guided by calculating $\triangle AIC =
AIC_{1} - AIC_{2}$ and $\triangle BIC = BIC_{1} - BIC_{2}$.  Positive
values of $\triangle AIC, \triangle BIC$ express a preference for model 2
over model 1.

@@

\section{Discussion}
The presence of a \PL\ \PS\ has implications for the detection of
narrow frequency band oscillations against such a background emission,
for both non-automated and automated methods.  These are discussed in
Sections \ref{ssec:corseis} and \ref{sec:oscdetect}.  Further, the
\PL\ Fourier spectrum in coronal emission poses questions about how
that emission is formed.  A hypothesis regarding the formation of this
power law spectrum is presented in Section \ref{ssec:nplps}.

@@

Section \ref{sec:anal} demonstrates the presence of an approximate
\PL\ \PS\ signal in two of the most commonly used wavebands for
coronal seismology, SDO-AIA 171\AA\ and 193\AA.  The observed spectra
generally show a \PL-like behavior at time-scales of interest in
coronal seismology, and longer.  Within the confines of the models we
have chosen, coronal moss regions show the largest contribution from a
non \PL\ \PS\ source over a relatively limited range of frequencies.
The frequencies at which the lognormal contribution is larger than the
underlying power-law distribution could be used to define an average
frequency range within which the majority contribution to the overall
Fourier power is not associated with the underlying power-law
distribution.  However, the \Fps\ in this range would still have to
analyzed using both the power-law and lognormal contributions to the
overall power, and better estimates to the power-law parameters will
be obtained if the full frequency range of the observations are used.

The presence of a non \PL\ contribution to the \Fps\ does not change
the fact that the background emission is essentially power-law like.
For the frequencies that have been of interest in coronal seismology,
the background \PS\ is therefore scale free on average.  If there is
no time-scale that can be used to remove a background trend, then the
time-series has to be analyzed without this processing step.  However,
a lack of awareness of the background \PL\ \PS\ nature of the emission
can cause problems in attempting to analyze for the presence of narrow
frequency band oscillations, as the following example demonstrates.

\begin{figure}
\epsscale{.80}
\plotone{white_red_compare.eps}
\caption{Comparison of the effect of assuming a white or
  \PL\ \PS\ background on the detection of an oscillatory signal for
  simulated time-series.  Plot (a) shows the simulated time-series,
  generated from a \protect\PS\ \protect$P(f)\propto f^{-1.77}$ and no
  explicit oscillation included.  Plot (b) shows the wavelet power
  spectrum with the cone-of-influence (shaded area) and regions above
  the 95\% confidence level, assuming a white-noise (Gaussian)
  background .  Plot (c) shows the global wavelet \protect\PS\ for
  this wavelet transform.  Plots (d) and (e) are the same as plots (b)
  and (c) under the assumption of a
  \protect\PL\ \protect\PS\ background.}
\label{fig:comparison}
\end{figure}

@@

The discussion of Section \ref{ssec:corseis} shows that \PL\ power
spectra have a powerful effect on the claims of a detection of
narrow-frequency band oscillations in single time-series.  When
looking at extended regions of coronal imaging data, evidence for the
presence of a {\it wave} in the corona is strengthened if it can be
shown that narrow frequency-band oscillations occur significantly
above the background signal in several neighboring pixels.  Spatial
extent is the key feature to claim of a detected wave.  Coronal
seismology derives its observational evidence from such detections,
and automated detection algorithms hold out the hope of greatly
increasing the number of oscillating regions detected.

@@

As has been shown above, the assumption of a Gaussian-distributed
(white) noise when a \PL\ \PS\ is actually present, coupled with too
low a confidence level, can lead to misleading results when looking
for oscillatory signals.  Many wave detection algorithms do make this
assumption, for example \cite{2004SoPh..223....1D},
\cite{2007SoPh..241..397N}, \cite{2008SoPh..248..395S},
\cite{2010SoPh..264..403I} and \cite{2013SoPh..286..405C}.  Such
approaches have yet to be tested assuming a background \PL\ \PS, and
so their efficacy is unknown.  However, \cite{2004SoPh..223....1D} and
\cite{2008SoPh..248..395S} are wavelet-based approaches, and the
discussion Section \ref{ssec:corseis} does suggest that a background
\PL\ \PS\ will make a significant difference to the number of wave
detections found in the data.

@@

\subsection{``Excess'' emission}\label{ssec:excess}
The models fits of Section \ref{sec:anal} indicate that equation
\ref{eqn:pwrlaw} is preferred over equation \ref{eqn:pwrlawbump} as
the superior description of the observed Fourier \PS. The
moss region shows the greatest contribution from the lognormal
distribution $G(\nu)$ over the background \PL.
\cite{2005ApJ...624L..61D} show that it is possible to leak
oscillatory power from lower in the atmosphere to the upper reaches of
the atmosphere through the simple expedient of tilting the field line.
This changes the acoustic cutoff frequency and so allows wave energy
to propagate up in to the upper atmosphere.  If spectral model $M_{2}$
represents conditions in the solar atmosphere, then it should be
possible to infer a distribution of field line angles with the solar
surface using \cite{2005ApJ...624L..61D} and the observed power
distribution $G(\nu)$.  This would constrain the distribution of field
line angles in the lower atmosphere in different regions of the solar
surface.

Another possible cause of the excess emission is the appearance of
low-temperature emission lines in the AIA passband.  Such lines are
more likely to be due to processes lower down in the solar atmosphere
where the amplitude of three and five minute oscillations is larger.
This is supported by three dimensional magnetohydrodynamic models of
the quiet Sun studied by \cite{2011ApJ...743...23M}.  It is shown that
lower temperature lines can be formed in quiet Sun areas that appear
in the AIA 171\AA\ and 193\AA\ wavebands. \cite{2011ApJ...743...23M}
find that the AIA 193\AA\ has more significant contributions from
non-dominant lines when compared to AIA 171\AA.  If this were the
case, then one would expect that the maximum of the ratio between
$G(\nu)/P_{1}(\nu)$ (see Figure \ref{fig:fit171193} and Table
\ref{tab:parameters}) would be higher for the AIA 193\AA\ \PS\ than
for the AIA 171\AA \PS, which is not observed.  However,
\cite{2011ApJ...743...23M} also note that their results are also quite
sensitive to the abundances used in their simulations, which may
explain the differences between their simulations and the observations
presented here.

\subsection{Nature of the \protect\PL\ \protect\PS}\label{ssec:nplps}
The first contribution to both models $P_{0}$ and $P_{i}$ is a
\PL-like \PS.  It is present in both wavebands studied and in all the
regions, and so parsimony suggests that the mechanism of its creation
is both similar and ubiquitous in all parts of the solar atmosphere.
Further, \cite{2014AA...563A...8A} show that a \PL\ \PS\ is present in
coronal active region and quiet Sun time-series over the frequency
range 0.01 - 1 mHz, overlapping with the frequency studied in this paper.

We hypothesize that the \PL\ \PS\ is due to the sum of a distribution
of a large number of emission events having different amounts of
emission. \cite{2011soca.book.....A} describes how a \PL\ \PS\ may
obtained from such a distribution, and that argument is outlined
below.

>>>>

\begin{abstract}
  The dynamics of regions of the solar corona are investigated using
  AIA 171\AA\ and 193\AA\ data.  It is commonly assumed that coronal
  time-series are well described by the sum of a long time-scale
  background trend plus Gaussian-distributed noise, with some specific
  locations also showing an oscillatory signal.  It is shown that the
  \mFpa\ in all regions follows an approximate \PL\ behaviour.  This
  average behavior is inconsistent with this commonly held assumption.
  The implications of this discovery to the field of coronal
  seismology and automated detections of oscillations is discussed.
  The observed \PL\ \PS\ can be formed by summing a distribution of
  exponentially decaying emission events along the line of sight.
  This is consistent with the idea that the solar atmosphere is heated
  everywhere by small energy deposition events.
\end{abstract}

@@

\section{Introduction}\label{sec:int}
Coronal seismology is the study of oscillatory phenomena in the solar
corona.  First suggested by \cite{1970PASJ...22..341U}, the practice
of coronal seismology attempts to locate oscillatory phenomena in the
solar corona, identify the wave modes present, and then use
theoretical descriptions of those wave modes to infer the physical
conditions of the solar corona.  The practical application of coronal
seismological ideas began in earnest with observations of wave modes
by SOHO/EIT \citep{1998ApJ...501L.217D, 1999SoPh..186..207B} and TRACE
\citep{1999ApJ...520..880A} (see also \cite{lrsp-2005-3},
\cite{2012RSPTA.370.3193D} for more extensive reviews of coronal
seismology).  Since then, many papers have been published describing
oscillatory phenomena in the corona and their interpretation in terms
of theoretically known wave modes.

@@

The relative scarcity of observations of coronal oscillations has
prompted efforts to create automated oscillation detection algorithms.
The need for an automated oscillation detection algorithm has been
exacerbated by the large and rapidly growing amount of AIA data.
There have been several attempts at designing such algorithms.
\cite{2004SoPh..223....1D} describe the design of an automated
oscillation-detection algorithm based on wavelet analysis. The
algorithm finds significant wave packets ranging from single to
multiple wave cycles in duration, by a wavelet power/confidence level
comparison against the null hypothesis that a given time series is
Gaussian-distributed noise.  Pixels with significant oscillatory
content are grouped manually.  \cite{2007SoPh..241..397N} take a
similar approach, using a thresholded fast Fourier transform to find
locations in TRACE data that may support an oscillatory signal. The
threshold level is defined as three to four times the average FFT
power; if the maximum FFT power is above this level then the frequency
at which that power occurs is assumed to be real.
\cite{2010SoPh..264..403I} assume that an oscillatory signal is
present in each location in the datacube and then use a Bayesian-based
treatment to calculate the probability that the frequency has a
particular value.  This algorithm relies on subtracting a background
trend from the time-series being tested, and assumes that the noise is
Gaussian distributed.

The above algorithms precipitate detections based on the strength of
the signal of an oscillation on a pixel by pixel basis, and then group
these pixels together using some set of criteria.  The automated
detection algorithm of \cite{2008SoPh..248..395S} begins by
identifying candidate oscillatory regions as those whose time-series
of emission show a high variance \citep{2003SoPh..213..103G} (under
the implicit assumption that the time-series has an approximately
constant mean value).  Detections are based on wavelet filtering of
these regions in all three dimensions of the data cube simultaneously,
with the implicit assumption that the noise is Gaussian-distributed.
The algorithm of \cite{2008SoPh..252..321M} differs from the previous
algorithms: it begins by Fourier transforming the entire data cube,
and calculating the coherence of neighboring pixels in narrow
frequency bands, and filtering the results. The null hypothesis here
is that the time series is pure Gaussian noise, with the additional
assumption that pairs of noisy time-series have low coherence, and so
can be rejected.  In this algorithm, the spatial extent of the
coherence of the oscillatory signal is the key identifier of a wave
process.

@@

Section \ref{sec:obs} describes the observations used, while Section
\ref{sec:anal} describes the method of analysis employed and presents
the results.  Section \ref{sec:discuss} discusses the implication of
these results for coronal seismology and the heating of the solar
atmosphere.  Section \ref{sec:conc} summarizes the discussion and
outlines future work.

\section{Observations}\label{sec:obs}
AIA observes images of the Sun in multiple wavebands simultaneously
and continuously, at high cadence (12 seconds) and at high spatial
resolution (0.6 arcseconds per pixel at the Sun).  These data enable
detailed comparisons between phenomena seen in multiple wavebands, and
are therefore ideal for assessing the frequency content of the solar
atmosphere.  The data was acquired using the Lockheed Martin Solar
Astrophysics cutout service (http://lmsal.com/get\_aia\_data/).  Six
hours of image data in the time range 2012-09-23 00:00 - 06:00 UT, at
the full 12 second cadence, in the 171\AA\ and 193\AA\ wavebands is
used.  These wavebands were selected because previous studies in
similar wavebands (TRACE 171\AA\ and 193\AA) show the presence of
coronal oscillations.  The cutout of the Sun selected covers two
adjacent $\beta\gamma$ regions NOAA AR 11575 and AR 11577.  This
cutout was selected for two reasons.  First, it is quiescent in that
there were no X-ray flares or other large-scale disturbances (for
example, filament eruptions or rearrangments of long bright coronal
loops) over the spatial extent of the cutout within the time range
(Figure \ref{fig:loc171193}).  Therefore, any variations in the plasma
properties cannot be ascribed to large-scale disturbances.  Second,
the selected cutout region contains a sunspot, and sunspots are known
to be locations over which three minute oscillations have been
detected by other instruments \citep{2002A&A...387L..13D}.

The downloaded cutout data was prepared for analysis using the
SolarSoft / IDL routines READ\_SDO and AIA\_PREP.  These procedures
convert the downloaded level 1.0 FITS cutout files to level 1.5 FITS
files.  This involves translating, scaling and rotating the images so
they have the same sun-center, image scale with solar north in the
same direction.  All further processing from this point was performed
in the SunPy 0.4 (http://www.sunpy.org) data analysis environment.
Images were de-rotated to compensate for solar rotation, based on the
center of the field of view of each image.  After de-rotation, each
image layer was co-registered with the image half way through the
dataset, at approximately 03:00 UT (Figure \ref{fig:loc171193}).

\section{Analysis}\label{sec:anal}
We wish to analyze the frequency content of these resulting datacubes
as a function of spatial location.  Four locations were chosen in the
data representing four different types of physical locations in the
solar atmosphere.  These were a quiet Sun region, a region that lies
on top of a sunspot, a footpoint region, and a coronal moss region.
Figure \ref{fig:loc171193} shows the location of the regions on sample
images from the time range considered.

@@

Consider the emission from a single pixel, $I(t)$.  The Fourier power
spectrum for this emission was calculated as follows.  First, the
time-series was normalized by calculating $(I(t) - \langle I(t)
\rangle)/\langle I(t) \rangle$. Secondly, the normalized time-series
was apodized using the Hanning window, reducing ringing effects in the
\PS.  The full 12 second cadence is used, yielding time series of 1800
samples.  The full spatial resolution is also retained in order to
obtain fine detail on the variation of frequency content as a function
of location.  Figure \ref{fig:compare171193} show example power
spectra, plotted using a log-log scale, from a single location inside
each of the regions shown in Figure \ref{fig:loc171193}.  The shape of
the power spectra indicate that the Fourier power approximately
follows a \PL\ at lower frequencies, and flattens out at higher
frequencies.

@@

\begin{figure}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_loopfootpoints.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_loopfootpoints.hanning.relative.power_spectra_distributions.eps}
}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_moss.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_moss.hanning.relative.power_spectra_distributions.eps}
}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_qs.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_qs.hanning.relative.power_spectra_distributions.eps}
}
\centerline{
\epsscale{0.8}\plottwo{shutdownfun3_6hr_disk_1.5_171_sunspot.hanning.relative.power_spectra_distributions.eps}{shutdownfun3_6hr_disk_1.5_193_sunspot.hanning.relative.power_spectra_distributions.eps}
}
\caption{Distribution of Fourier power at some sample frequencies as a
function of AIA waveband and location.}
\label{fig:dist171193}
\end{figure}
Figure \ref{fig:dist171193} shows the probability distribution of the
Fourier power of the pixels in each region at five selected
frequencies, for all the pixels in each region.  These distributions
are centrally peaked, show a slightly heavier tail towards lower
Fourier powers (negative skew), are slightly broader when compared to
a Gaussian distribution, and are all unimodal.  These observations
guide the choice of how to average the \PS\ over each of the selected
region.  The nature of these distributions suggest that the arithmetic
mean of the Fourier power is biased by the very largest powers.
Therefore, the mean value of the logarithm of the Fourier power is a
better description of the range of values in the data (this is
equivalent to the geometric mean of the Fourier power).  The \PA\ used
below are calculated from the mean value of the logarithm of the
Fourier power.

@@

The (geometric) \mFpa\ are shown in Figure \ref{fig:fit171193} for
each of the physical regions considered.  It is clear that, in
general, the \mFpa\ exhibit power-law like characteristics.  The
results for the quiet Sun, loop footpoints and sunspot regions suggest
a \PL\ \PS.  This can be modeled as
\begin{equation}
\label{eqn:pwrlaw}
\mbox{Model $M_{1}$}: P_{1}(\nu) = A\nu^{-n} + C,
\end{equation}
where $\nu$ is the frequency, $A>0$ is a proportionality constant and
$n>0$ is the \PL\ index.  The quantity $C>0$ models the high-frequency
/ low power end of the spectrum where the detection properties of the
detector apparatus are assumed to dominate the observations.

@@

Model selection is implemented using the Akaike Information Criterion
(AIC) and the Bayesian Information Criterion (BIC).  The AIC is defined as
\begin{equation}\label{eqn:aic}
AIC \equiv -2 \ln L_{max} - 2k
\end{equation}
where $L_{max}$ is the maximum likelihood achievable by the model, and
$k$ is the number of parameters in the model ($k=3$ for Model 1, and
$k=6$ for Model 2).  The BIC is defined as
\begin{equation}\label{eqn:bic}
BIC \equiv -2 \ln L_{max} - k\ln N
\end{equation}
where $N$ is the number of data points used in the fit (in this case
$N=899$, the number of non-zero frequencies of the Fourier power
spectrum).  Model selection is guided by calculating $\triangle AIC =
AIC_{1} - AIC_{2}$ and $\triangle BIC = BIC_{1} - BIC_{2}$.  Positive
values of $\triangle AIC, \triangle BIC$ express a preference for model 2
over model 1 \citep{2007MNRAS.377L..74L, WICS:WICS199}.

@@

\section{Discussion}\label{sec:discuss}
The presence of a \PL\ \PS\ has implications for the detection of
narrow frequency band oscillations against such a background emission,
for both non-automated and automated methods.  These are discussed in
Sections \ref{ssec:corseis} and \ref{sec:oscdetect}.  Further, the
\PL\ Fourier spectrum in coronal emission poses questions about how
that emission is formed.  Section \ref{ssec:excess} discusses possible
reasons for the localized contribution component $G(\nu)$.  A
hypothesis regarding the formation of this power law spectrum is
presented in Section \ref{ssec:nplps}.

@@

Section \ref{sec:anal} demonstrates the presence of an approximate
\PL\ \PS\ signal in two of the most commonly used wavebands for
coronal seismology, SDO/AIA 171\AA\ and 193\AA.  The observed spectra
generally show a \PL-like behavior at time-scales of interest in
coronal seismology, and longer.  Within the confines of the models we
have chosen, coronal moss regions show the largest contribution from a
non \PL\ \PS\ source over a relatively limited range of frequencies.
The frequencies at which the lognormal contribution is larger than the
underlying power-law distribution could be used to define an average
frequency range within which the majority contribution to the overall
Fourier power is not associated with the underlying power-law
distribution.  However, the \Fps\ in this range would still have to
analyzed using both the power-law and lognormal contributions to the
overall power, and better estimates to the power-law parameters will
be obtained if the full frequency range of the observations are used.

The presence of a non \PL\ contribution to the \Fps\ does not change
the fact that the background emission is essentially power-law like.
For the frequencies that have been of interest in coronal seismology,
the background \PS\ is therefore scale free on average.  If there is
no time-scale that can be used to remove a background trend, then the
time-series has to be analyzed without this processing step.  However,
a lack of awareness of the background \PL\ \PS\ nature of the emission
will cause significant problems in attempting to analyze for the
presence of narrow frequency band oscillations, as the following
example demonstrates.

\begin{figure}
\epsscale{0.80}
\plotone{white_red_compare.eps}
\caption{Comparison of the effect of assuming a white or
  \PL\ \PS\ background on the detection of an oscillatory signal for
  simulated time-series.  Plot (a) shows the simulated time-series,
  generated from a \protect\PS\ \protect$P(f)\propto f^{-1.77}$ and no
  explicit oscillation included.  Plot (b) shows the wavelet power
  spectrum with the cone-of-influence (shaded area) and regions above
  the 95\% confidence level, assuming a white-noise (Gaussian)
  background .  Plot (c) shows the global wavelet \protect\PS\ for
  this wavelet transform.  Plots (d) and (e) are the same as plots (b)
  and (c) under the assumption of a
  \protect\PL\ \protect\PS\ background.}
\label{fig:comparison}
\end{figure}

@@

The discussion of Section \ref{ssec:corseis} shows that \PL\ power
spectra have a powerful effect on the claims of a detection of
narrow-frequency band oscillations in single time-series.  When
looking at extended regions of coronal imaging data, evidence for the
presence of a propagating wave in the corona is strengthened if it can
be shown that narrow frequency-band oscillations occur significantly
above the background signal in several neighboring pixels.  Spatial
extent is the key feature to claim of a detected wave.  Coronal
seismology derives its observational evidence from such detections,
and automated detection algorithms hold out the hope of greatly
increasing the number of oscillating regions detected.

@@

As has been shown above, the assumption of a Gaussian-distributed
(white) noise when a \PL\ \PS\ is actually present, coupled with too
low a confidence level, can lead to misleading results when looking
for oscillatory signals (Section \ref{ssec:corseis} and Figure
\ref{fig:comparison}).  Many wave detection algorithms do make this
assumption, for example \cite{2004SoPh..223....1D},
\cite{2007SoPh..241..397N}, \cite{2008SoPh..248..395S},
\cite{2010SoPh..264..403I} and \cite{2013SoPh..286..405C}.  Such
approaches have yet to be tested assuming a background \PL\ \PS, and
so their efficacy is unknown.  However, \cite{2004SoPh..223....1D} and
\cite{2008SoPh..248..395S} are wavelet-based approaches, and the
discussion Section \ref{ssec:corseis} does suggest that a background
\PL\ \PS\ will make a significant difference to the number of wave
detections found in the data.

@@

\subsection{``Excess'' emission}\label{ssec:excess}
The models fits of Section \ref{sec:anal} indicate that equation
\ref{eqn:pwrlawbump} is preferred over equation \ref{eqn:pwrlaw} as
the superior description of the observed Fourier \PS. The moss region
shows the greatest contribution from the lognormal distribution
$G(\nu)$ over the background \PL.  \cite{2005ApJ...624L..61D} show
that it is possible to leak oscillatory power from lower in the
atmosphere to the upper reaches of the atmosphere through the simple
expedient of tilting the field line.  This changes the acoustic cutoff
frequency and so allows wave energy to propagate up in to the upper
atmosphere.  If spectral model $M_{2}$ represents conditions in the
solar atmosphere, then it should be possible to infer a distribution
of field line angles with the solar surface using
\cite{2005ApJ...624L..61D} and the observed power distribution
$G(\nu)$.  This would constrain the distribution of field line angles
in the lower atmosphere in different regions of the solar surface.

Another possible cause of the excess emission is the appearance of
low-temperature emission lines in the AIA passband.  Such lines are
more likely to be due to processes lower down in the solar atmosphere
where the amplitude of three and five minute oscillations is larger.
This is supported by three dimensional magnetohydrodynamic models of
the quiet Sun studied by \cite{2011ApJ...743...23M}.  It is shown that
lower temperature lines can be formed in quiet Sun areas that appear
in the AIA 171\AA\ and 193\AA\ wavebands. \cite{2011ApJ...743...23M}
find that the AIA 193\AA\ has more significant contributions from
non-dominant lines when compared to AIA 171\AA.  If this were the
case, then one would expect that the maximum of the ratio between
$G(\nu)/P_{1}(\nu)$ (see Figure \ref{fig:fit171193} and Table
\ref{tab:parameters}) would be higher for the AIA 193\AA\ \PS\ than
for the AIA 171\AA\ \PS, which is not observed.  However,
\cite{2011ApJ...743...23M} also note that their results are also quite
sensitive to the abundances used in their simulations, which may
explain the differences between their simulations and the observations
presented here.

\subsection{Nature of the \protect\PL\ \protect\PS}\label{ssec:nplps}
The first contribution to both models $M_{1}$ and $M_{2}$ is a
\PL-like \PS.  It is present in both wavebands studied and in all the
regions, and so parsimony suggests that the mechanism of its creation
is both similar and ubiquitous in all parts of the solar atmosphere.
Further, \cite{2014AA...563A...8A} show that a \PL\ \PS\ is present in
coronal active region and quiet Sun time-series over the frequency
range 0.01 - 1 mHz, overlapping with the frequency studied in this paper.

We hypothesize that the \PL\ \PS\ is due to the sum of a distribution
of a large number of events having different amounts of
emission. \cite{2011soca.book.....A} describes how a \PL\ \PS\ may
obtained from such a distribution, and that argument is outlined
below.
